Visualisation of Brain Statistics with R-packages _ggseg_ and _ggseg3d_

### 2020-04-21 codethrough.Rmd
new codethrough

---
title: "Visualisation of Brain Statistics with R-packages _ggseg_ and _ggseg3d_"
subtite: "code through"
output: html_notebook
---

@@

```{r, size='small'}
file_path <- "data/aparc.volume.table"

@@

```{r "figure7-show", out.width='30%',fig.show='hold',fig.ncol = 3}
# remotes::install_github("LCBC-UiO/ggseg3d")
library(ggseg3d)

@@

```{r out.width='80%'}
# Select surface and hemisphere, and then unnest to inspect the atlas data
dk_3d %>%
  filter(surf == "inflated" & hemi == "right") %>%
  unnest(ggseg_3d) %>%
  head(5)
```

@@

```{r 'figure9', out.width='60%', echo=F, eval=T, fig.cap="(ref:figure9-cap)"}
include_plotly(fig9, "msc_ggseg_files/figure-latex/figure9.png")
```

@@

invisible(ggsave(filename = "msc_ggseg_files/figure-latex/figure10ab.png", 
                 plot = ggsegs_p, device = "png"))
orca(desterieux_p, file = "msc_ggseg_files/figure-latex/figure10c.png", format = "png")
orca(icbm_p, file = "msc_ggseg_files/figure-latex/figure10d.png", format = "png")

include_graphics(c(
  "msc_ggseg_files/figure-latex/figure10ab.png",
  "msc_ggseg_files/figure-latex/figure10c.png",
  "msc_ggseg_files/figure-latex/figure10d.png"
))
```

>>>>

---
title: "Visualisation of Brain Statistics with R-packages _ggseg_ and _ggseg3d_"
subtite: "code through"
output: html_notebook
bibliography: references.bib
---

@@

```{r, size='small'}
library(dplyr)
file_path <- "data/aparc.volume.table"

@@

```{r "figure7-show", out.width='30%',fig.show='hold',fig.ncol = 3}
# remotes::install_github("LCBC-UiO/ggseg3d")
library(ggseg3d)
library(plotly)

@@

```{r out.width='80%'}
# Select surface and hemisphere, and then unnest to inspect the atlas data
dk_3d %>%
  filter(surf == "inflated" & hemi == "right") %>%
  tidyr::unnest(ggseg_3d) %>%
  head(5)
```

@@

```{r 'figure9', out.width='60%', echo=F, eval=T, fig.cap="(ref:figure9-cap)"}
# Convenience function to easily add plotly images to rmarkdown
include_plotly <- function(plot, file){
  orca(plot, file = file, format = "pdf")
  knitr::include_graphics(file)
}

include_plotly(fig9, "figure9.pdf")
```

@@

invisible(ggsave(filename = "figure10ab.pdf", 
                 plot = ggsegs_p, device = "pdf"))
orca(desterieux_p, file = "figure10c.pdf", format = "pdf")
orca(icbm_p, file = "figure10d.pdf", format = "pdf")

knitr::include_graphics(c(
  "figure10ab.pdf",
  "figure10c.pdf",
  "figure10d.pdf"
))
```

### 2020-04-21 msc_ggseg.Rmd
new codethrough

include_plotly <- function(plot, file){
  orca(plot, file = file, format = "png")
  knitr::include_graphics(file)
}

@@

```{r "figure7", message=FALSE, echo=F, eval=TRUE, out.width='30%',fig.show='hold',fig.ncol = 3, fig.cap='(ref:figure7-cap)'}
orca(fig7l, file = "msc_ggseg_files/figure-latex/figure7l.png", format = "png")
orca(fig7m, file = "msc_ggseg_files/figure-latex/figure7m.png", format = "png")
orca(fig7r, file = "msc_ggseg_files/figure-latex/figure7r.png", format = "png")

include_graphics(c("msc_ggseg_files/figure-latex/figure7l.png",
                   "msc_ggseg_files/figure-latex/figure7m.png",
                   "msc_ggseg_files/figure-latex/figure7r.png"))
```

@@

```{r 'figure8', out.width='30%', echo=FALSE, fig.cap="(ref:figure8-cap)", fig.show='hold', fig.ncol = 3}
orca(fig8l, file = "msc_ggseg_files/figure-latex/figure8l.png", format = "png")
orca(fig8m, file = "msc_ggseg_files/figure-latex/figure8m.png", format = "png")
orca(fig8r, file = "msc_ggseg_files/figure-latex/figure8r.png", format = "png")

include_graphics(c(
  "msc_ggseg_files/figure-latex/figure8l.png",
  "msc_ggseg_files/figure-latex/figure8m.png",
  "msc_ggseg_files/figure-latex/figure8r.png"))

@@

```{r 'figure9', out.width='60%', echo=F, eval=T, fig.cap="(ref:figure9-cap)"}
include_plotly(fig9, "msc_ggseg_files/figure-latex/figure9.png")
```

@@

invisible(ggsave(filename = "msc_ggseg_files/figure-latex/figure10ab.png", 
                 plot = ggsegs_p, device = "png"))
orca(desterieux_p, file = "msc_ggseg_files/figure-latex/figure10c.png", format = "png")
orca(icbm_p, file = "msc_ggseg_files/figure-latex/figure10d.png", format = "png")

include_graphics(c(
  "msc_ggseg_files/figure-latex/figure10ab.png",
  "msc_ggseg_files/figure-latex/figure10c.png",
  "msc_ggseg_files/figure-latex/figure10d.png"
))
```

>>>>

include_plotly <- function(plot, file){
  orca(plot, file = file, format = "pdf")
  knitr::include_graphics(file)
}

@@

```{r "figure7", message=FALSE, echo=F, eval=TRUE, out.width='30%',fig.show='hold',fig.ncol = 3, fig.cap='(ref:figure7-cap)'}
orca(fig7l, file = "msc_ggseg_files/figure-latex/figure7l.pdf", format = "pdf")
orca(fig7m, file = "msc_ggseg_files/figure-latex/figure7m.pdf", format = "pdf")
orca(fig7r, file = "msc_ggseg_files/figure-latex/figure7r.pdf", format = "pdf")

include_graphics(c("msc_ggseg_files/figure-latex/figure7l.pdf",
                   "msc_ggseg_files/figure-latex/figure7m.pdf",
                   "msc_ggseg_files/figure-latex/figure7r.pdf"))
```

@@

```{r 'figure8', out.width='30%', echo=FALSE, fig.cap="(ref:figure8-cap)", fig.show='hold', fig.ncol = 3}
orca(fig8l, file = "msc_ggseg_files/figure-latex/figure8l.pdf", format = "pdf")
orca(fig8m, file = "msc_ggseg_files/figure-latex/figure8m.pdf", format = "pdf")
orca(fig8r, file = "msc_ggseg_files/figure-latex/figure8r.pdf", format = "pdf")

include_graphics(c(
  "msc_ggseg_files/figure-latex/figure8l.pdf",
  "msc_ggseg_files/figure-latex/figure8m.pdf",
  "msc_ggseg_files/figure-latex/figure8r.pdf"))

@@

```{r 'figure9', out.width='60%', echo=F, eval=T, fig.cap="(ref:figure9-cap)"}
include_plotly(fig9, "msc_ggseg_files/figure-latex/figure9.pdf")
```

@@

invisible(ggsave(filename = "msc_ggseg_files/figure-latex/figure10ab.pdf", 
                 plot = ggsegs_p, device = "pdf"))
orca(desterieux_p, file = "msc_ggseg_files/figure-latex/figure10c.pdf", format = "pdf")
orca(icbm_p, file = "msc_ggseg_files/figure-latex/figure10d.pdf", format = "pdf")

include_graphics(c(
  "msc_ggseg_files/figure-latex/figure10ab.pdf",
  "msc_ggseg_files/figure-latex/figure10c.pdf",
  "msc_ggseg_files/figure-latex/figure10d.pdf"
))
```
